---
title: "Day 11 Practice/Homework"
output: html_document
---
# I was not sure exactly what you were asking for but I tried to make a function using both of the parts you listed 
Make a function that:
  1. Runs the code in every .R script in a directory
    - `dir()`
    - `source()`
    
```{r}
file.sources = list.files(c("C:/Desktop/PSYC 798W"), 
    pattern="\\.Rmd$", full.names=TRUE, 
    ignore.case=FALSE)

for (f in list.files(pattern="\\.Rmd$")) {
    source(f)
}
# I tried both of these functions but both of them gave me an empty set of values. I would theoretically want to then apply some kind of change/adjustment to all of "f" or the sourced files

```
    
  
  2. Returns the names of all the files you ran (without the .R extension)
    - `sub()` or `gsub()`
    
```{r}
grep(pattern="-\\.Rmd$", x, ignore.case = FALSE, perl = FALSE, value = FALSE, fixed = FALSE, useBytes = FALSE, invert = FALSE)

# This function is trying to return everything that is not .Rmd but it still gives me nothing even though it runs
```

    
  3. Returns the names of all functions you loaded (assuming the .R scripts have functions
    - HARD WAY 
      - `readLines()`
      - `?
      gsub()`
    - easier way
      - `ls()`
      
```{r}

readLines(con = "stdin("-\\.Rmd$"), n = -1L, ok = TRUE, warn = TRUE,
          encoding = "unknown", skipNul = FALSE)

ls(name, pos = -1L, envir = as.environment(pos),
   all.names = TRUE, pattern)

# this would work as long as there is no problem returning files back to the current enviornment



```



```

```
