---
output: pdf_document
---
Final Project: "Fresh Food Accessibilty within the Washington DC Area"

# The overall objectives of this project are to 1) better understand the relative densities of Farmers Markets in counties in and around Washington DC, 2) determine any potential relationships between store density/abundance and the demographic make-up of the county itself and 3) visualize differences on a county map of the region


```{r}

#Step 1: Narrow and connect three seperate data frames  

#1a Created a data frame with select columns and counties from the "stores" Excel sheet 

mystores <- read.csv("~/Desktop/PSYC 798W/FoodAccess_USDA_Stores.csv")
colnames(mystores)
mynames <- c("FIPS", "State", "County", "Groc07", "Groc11","GrChange","GrPop07","GrPop11", "GrPopChange", "Super07", "Super11", "SuChange", "SuPop07", "SuPop11" ,"SuPopChange", "Conv07", "Conv11" , "ConChange" , "ConPop07", "ConPop11", "ConPopChange", "Special07","Special11", "SpChange", "SpPop07", "SpPop11","SpPopChange", "Snap08","Snap12","SnChange", "SnPop08", "SnPop12", "SnPopChange", "WIC08", "WIC12","WChange","WPop08", "WPop12", "WPopChange") 
colnames(mystores) <- mynames
head(mystores)
mystores$FIPS <- as.factor(mystores$FIPS)
summary(mystores)
mystores[28:39]<-list(NULL) 
head(mystores)
DCsubstores <- mystores[mystores$County %in% c("Ann Arundel", "Charles","Prince George's", "Montgomery", "Howard", "Loudoun", "Arlington", "Alexandria", "Falls Church", "Fairfax", "Prince William", "Fauquier", "District of Columbia"), ]
DCsubstores
DCsubstores2 <- DCsubstores[DCsubstores$State %in% c("MD", "VA", "DC"), ]
DCsubstores2

#1b Created a second data frame with the columns concerning Farmers Markets from the "local" Excel spread sheet. Changed column labels to match first dataset. 

mymarket <- read.csv("~/Desktop/PSYC 798W/FoodAccess_USDA_Local.csv")
DCsubmarket <- mymarket[mymarket$County %in% c("Ann Arundel", "Charles","Prince George's", "Montgomery", "Howard", "Loudoun", "Arlington", "Alexandria", "Falls Church", "Fairfax", "Prince William", "Fauquier", "District of Columbia"), ]
DCsubmarket2 <- DCsubmarket[DCsubmarket$State %in% c("MD", "VA", "DC"), ]
colnames(DCsubmarket2)
DCsubmarket2[1:2] <- list(NULL)
DCsubmarket2[2:6] <- list(NULL)
DCsubmarket2[8:43] <- list(NULL)
mynames2 <- c("County", "Farm09", "Farm13", "FaChange","FaPop09", "FaPop13","FaPopChange")
colnames(DCsubmarket2) <- mynames2
colnames(DCsubmarket2)
DCsubmarket2

#1c Created a thid data frame with the columns concerning population demographic data from "socioeconomic" Excel spread sheet. Changed column labels

mydemo<- read.csv("~/Desktop/PSYC 798W/FoodAccess_USDA_socioeconomic.csv")
DCsubdemo <- mydemo[mydemo$County %in% c("Ann Arundel", "Charles","Prince George's", "Montgomery", "Howard", "Loudoun", "Arlington", "Alexandria", "Falls Church", "Fairfax", "Prince William", "Fauquier", "District of Columbia"), ]
DCsubdemo2 <- DCsubdemo[DCsubdemo$State %in% c("MD", "VA", "DC"), ]
colnames(DCsubdemo2)
DCsubdemo2[1:2] <- list(NULL)
DCsubdemo2[12:16] <- list(NULL)
mynames3 <- c("County", "WhitePop", "BlackPop", "HispanicPop","AsianPop", "AmIndianPop","IslanderPop","65yrs+","<18yrs", "MedianIncome","PovRate")
colnames(DCsubdemo2) <- mynames3
colnames(DCsubdemo2)
DCsubdemo2

#1d Merged all three data frames together 
subfinaltable <- merge(DCsubstores2,DCsubmarket2, by="County")
finaltable <-merge(subfinaltable, DCsubdemo2, by="County")
head(finaltable)
duplicated(finaltable) # This is telling me that there are no duplicates but there does seem to be some identical rows present after the merge. I left them in but am uncertian how they got there to begin with. 
finaltable
```

```{r}
#Step 2: Determine and visualize potential relationships between variable categories

#2a Is there a significant different in the number of Farmers Markets per county between 2009-2013
mytest <- t.test(finaltable$Farm09, finaltable$Farm13, paired = TRUE)
pval <- mytest$p.value
pval
# p=4.992888e-06, since p<.05, this relationship is SIGNIFICANT

#2b Is there a statistically significant difference in the number of Farmers Markets per person among counties?

mytest <- t.test(finaltable$FaPop09, finaltable$FaPop13, paired = TRUE)
pval <- mytest$p.value
pval
# p=0.0001007429. Since p<.05 this relationship is SIGNFICANT. 

#2c Is there a correlation between the total number of Farmers Markets  and the number of Convenience Stores within each county?

colnames(finaltable)
myFCONcor <- cor.test(finaltable[,29], finaltable[, 17])
pval <- myFCONcor$p.value
pval
library(compute.es)
corval <- myFCONcor$estimate
corval 

# p=0.2874723. Since p>.05 this relationship is NOT SIGNIFICANT
# r=0.2167734. This relationship has a very weak positive correlation. 

library(ggplot2)
ggplot(finaltable, aes(x=Farm13, y=Conv11)) +
    geom_point(shape=1) +    
    geom_smooth() +
    geom_text(aes(label=County),hjust=0, vjust=1)
# the graph works but the labels create suboptimal visualization. I tried instead to make VA counties red, MD counties green, and DC blue 
ggplot(finaltable, aes(x=Farm13, y=Conv11)) +  
    geom_smooth() +
    geom_point(aes(colour=State)) +
    scale_colour_manual(values=c("blue", "green","red"))

#2d Is there a correlation between the total number of Caucasians and the number of Farmers Markets in each county?

colnames(finaltable)
myFCAUcor <- cor.test(finaltable[,34], finaltable[, 29])
pval <- myFCAUcor$p.value
pval
library(compute.es)
corval <- myFCAUcor$estimate
corval 

# p=0.2906058. Since p>.05 this relationship is NOT SIGNIFICANT
# r=-0.2154027. This relationship has a very weak negative correlation.

ggplot(finaltable, aes(x=Farm13, y=WhitePop)) +  
    geom_smooth() +
    geom_point(aes(colour=State)) +
    scale_colour_manual(values=c("blue", "green","red"))

# 2e Is there a correlation between the total number of Farmers Markets  and the poverty rate within each county?

colnames(finaltable)
myFPOVcor <- cor.test(finaltable[,28], finaltable[, 43])
pval <- myFPOVcor$p.value
pval
library(compute.es)
corval <- myFPOVcor$estimate
corval 

# p=0.1602251. Since p>.05 this relationship is NOT SIGNIFICANT
# r=0.2836645 . This relationship has a very weak positive correlation.

ggplot(finaltable, aes(x=Farm13, y=PovRate)) +  
    geom_smooth() +
    geom_point(aes(colour=State)) +
    scale_colour_manual(values=c("blue", "green","red"))

# 2f Is there a correlation between the total number of Farmers Markets per person and the poverty rate within each county?

colnames(finaltable)
myFPPcor <- cor.test(finaltable[,32], finaltable[, 43])
pval <- myFPPcor$p.value
pval
library(compute.es)
corval <- myFPPcor$estimate
corval 

# p=0.5046669. Since p>.05 this relationship is NOT SIGNIFICANT
# r=0.1369589 . This relationship has a very weak positive correlation.

ggplot(finaltable, aes(x=FaPop13, y=PovRate)) +  
    geom_smooth() +
    geom_point(aes(colour=State)) +
    scale_colour_manual(values=c("blue", "green","red"))
```

```{r}
#Step 3: Attempt to visualize realtive farmers market abundance on map

install.packages("maps")
library(maps)
install.packages("mapproj")
library(mapproj)
map('usa')
map('county', region = c('maryland', 'virginia', 'district of columbia'))
map('state', lwd=2, add=TRUE) 

# I got this outline but hit a dead end. There appears to be a great way to merge the FIPS values for each county with the map but it is not readily apparent how to do this. I did find a method below that worked for obesity data but when I tried to use my own Farmers Market data, it did not work well and would not show it on the map outline created above.

#m.usa <- map_data("County")
#m.usa$id <- m.usa$subregion
#m.usa <- m.usa[ ,-5]
#names(m.usa)[5] <- 'region'

#myfinalmap <- data.frame(region = unique(m.usa$region),markets = rnorm(length(unique(m.usa$region)), 50, 10),stringsAsFactors = F)

#head(myfinalmap)

#ggplot(df, aes(map_id = region)) +
  #geom_map(aes(fill = markets), map = m.usa) + 
  #expand_limits(x = m.usa$long, y = m.usa$lat) +
  #coord_map()

```

```{r}
#Step 4: Print entire project as a more readable file. I do this by trying to Knit a PDF. The return is Line 160: "Error in contrib.url(repos, "source")" However, despite this error, all plots were "printed" as pdfs and pngs. 

library(knitr)

````

